Finding Quality Issues in SKOS Vocabularies

### 2012-03-23 background.tex
minor reformulation

% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions defining data model consistency. Such quality criteria are already well-established and have extensively been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, case studies~\cite{Soergel1995}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002,Elkin2002,Kless2010}.

>>>>

% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
Thus, in order to help vocabulary and application designers in improving the quality of SKOS vocabularies, we need to identify possible quality issues that go beyond integrity conditions defining data model consistency. Quality criteria for controlled vocabularies have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, case studies~\cite{Soergel1995}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002,Elkin2002,Kless2010}.
